The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-11-06 cordillera-climate.tex
Change section order
Small style corrections in introduction
General reread and polish
Get rid of personal shortcuts
Merge latex2rtf and pdflatex main files
Add a copernicus_rtf input file and replace to-do notes by regular footnotes. Using a copernicus_rtf package or class file did not seem to work with latex2rtf.
Implement corrections from Constantine
Implement corrections from Qiong
Add authors

% Copernicus manuscript
\documentclass[tc, ms, noauthor]{copernicus}

% Copernicus final print
%\documentclass[tc, noauthor]{copernicus}

@@

@@

% Recognize utf-8 special characters
\usepackage[utf8]{inputenc}

% Add to-do notes and enlarge right margin
\usepackage{todonotes}
\usepackage[left=54pt, top=81pt, textwidth=398pt, marginparsep=11pt, marginparwidth=93pt, textheight=625pt, footskip=30pt]{geometry}
\newcommand{\needref}[0]{\todo[color=cyan]{Reference needed}}
\newcommand{\arjen}[2][]{\todo[color=lime,{#1}]{\textbf{Arjen:} #2}}
\newcommand{\constantine}[2][]{\todo[color=yellow,{#1}]{\textbf{Constantine:} #2}}
\newcommand{\qiong}[2][]{\todo[color=pink,{#1}]{\textbf{Qiong:} #2}}
\newcommand{\julien}[2][]{\todo[color=lightgray,{#1}]{\textbf{Julien:} #2}}

% Personal shortcuts
\newcommand{\degC}[0]{\,\unit{\degree C} }
\newcommand{\masl}[0]{\,\unit{m a.s.l.} }

@@

% Title and authors
\title{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}
%\author{Julien Seguinot et al.}
%\affil{Department of Physical Geography and Quaternary Geology, Stockholm University, S-106 91 Stockholm, Sweden}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

@@

% Sections
\input{sections/abstract}
\input{sections/intro}
\input{sections/climate}
\input{sections/model}
\input{sections/results}
\input{sections/discuss}
\input{sections/concl}

@@

% Floats
\input{floats/tables}
\input{floats/figures}
\end{document}

>>>>

% Copernicus manuscript
\documentclass[tc, ms]{copernicus}

% Copernicus final print
%\documentclass[tc]{copernicus}

@@

% Copernicus-like latex2rtf compatible
%\input{copernicus_rtf}

@@

% Recognize utf-8 special characters
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% To-do footnotes
\newcommand{\needref}[0]{\footnote{Reference needed}}
\newcommand{\julien}[1]{\footnote{\textbf{Julien:} #1}}
\newcommand{\arjen}[1]{\footnote{\textbf{Arjen:} #1}}
\newcommand{\qiong}[1]{\footnote{\textbf{Qiong:} #1}}
\newcommand{\irina}[1]{\footnote{\textbf{Irina:} #1}}

@@

% Title
\title{The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum}
\runningtitle{Climate forcing for Cordilleran ice sheet simulations}

% Authors
\author[1]{Julien Seguinot}
\author[2]{Constantine Khroulev}
\author[3]{Irina Rogozhina}
\author[1]{Arjen Stroeven}
\author[1]{Qiong Zhang}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

% Affiliations
\affil[1]{Department of Physical Geography and Quaternary Geology, Stockholm University, Stockholm, Sweden}
\affil[2]{Geophysical Institute, University of Alaska Fairbanks, Fairbanks, AK, USA}
\affil[3]{Helmholtz Centre Potsdam, GFZ German Research Centre for Geosciences, Potsdam, Germany}

@@

% Sections
\input{sections/abstract}
\input{sections/intro}
\input{sections/model}
\input{sections/climate}
\input{sections/results}
\input{sections/discuss}
\input{sections/concl}

@@

% Floats
\newpage
\input{floats/tables}
\input{floats/figures}

% ----------------------------------------------------------------------
\end{document}
% ----------------------------------------------------------------------
